### 2020-02-07 ncov_euro.tex
add data av
Same tiny changes ☺

Our results emphasize the importance of propagating uncertainties in all components of \Ro, especially the shape of the generation-interval distribution in efforts to estimate \Ro at the outset of an epidemic.

>>>>

Our results emphasize the importance of propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution, in efforts to estimate \Ro at the outset of an epidemic.
